A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-20 paper/main.tex
revise table caption

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogues, non-speech
vocalizations (e.g. laughing or groaning) and script for the audio-description's
narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the
original audio.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume background speech (especially occurring during music or
continuous environmental noise) or low volume non-speech vocalizations which
were subjectively assessed to be incomprehensible for the audience were dropped,
too.
% intro for forced aligner
We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of the sentences, and the
onset and offset of each word and phoneme embedded in the transcribed sentences.
% preparing other inputs before forced alignment pronounciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

@@

\begin{table*}[tbp]
    \caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning. The category \texttt{sentences} comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
    It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly. The category \texttt{words} comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[btp]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie.
Overall 97 persons were identified.
Names are mostly identical to the names used in \citep{labs2015portrayed}.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% NLP
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
To automatically analyze linguistic features of each words in their corresponding
sentence, we employed the Python package spaCy \citep{spacy2} and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
Non-speech vocalizations were dropped from the sentences before analysis.
We performed analyses regarding part-of-speech (i.e. grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e. multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e. if the word is part of a stop list).

>>>>

\subsection*{Annotation procedure}
% preliminary annotations
Preliminary, manual orthographic transcriptions of dialogues, non-speech
vocalizations (e.g. laughter or groaning) and script for the audio-description's
narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
format.
% preparing annotation in Praat before forced alignment
% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a
couple of sentences was edited in Praat for manual validation against the
original audio.
% steps conducted
The following steps were done in several passes to iteratively improve the
quality of the data: approximate temporal onsets and offsets were corrected, and
intervals containing several sentences were split into intervals containing only
one sentence.
% dropping of sentences hard to understand
When two or more persons were speaking simultaneously the less dominant voice
was dropped. Low volume background speech (especially occurring during music or
continuous environmental noise) or low volume non-speech vocalizations which
were subjectively assessed to be incomprehensible for the audience were dropped,
too.
% intro for forced aligner
We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of the sentences, and the
onset and offset of each word and phoneme embedded in the transcribed sentences.
% preparing other inputs before forced alignment pronunciation dictionary
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
To enable the aligner to look up the phonemes embedded within each word, we
chose a German pronunciation dictionary provided by Prosodylab \citep
{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
pronunciation of phonemes.
% extending the dictionary with formerly unknown German words
To improve the detection rate of the automatic alignment, the dictionary was
manually updated with German words that occur in the stimuli but were originally
missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
% English words in the otherwise German stimulus
The pronunciation of English words and phonemes occurring in the otherwise
German audio track was taken from an English pronunciation dictionary (following
the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

@@

\begin{table*}[tbp]
    \caption{Overview of the annotation's content for the audio-only stimulus
that comprises the additional narrator. Counts are given for the whole stimulus
(\texttt{all}) and its individual segments used during fMRI scanning.
The category \texttt{sentences} comprises complete grammatical sentences which
are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
It also comprises questions (``do you want a chocolate?''), exclamations (``run
away!''), or non-speech vocalizations in quick succession (``ha, ha, ha''), or
in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when
speakers switch rapidly. The category \texttt{words} comprises each word or
non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[btp]
\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurs in the audio-description of the movie.
Overall 97 persons were identified.
Names are mostly identical to the names used in \citep{labs2015portrayed}.}
\label{tab:speakers}
\begin{tabular}{llllllllll}
\toprule
\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% natural luanguage processing (NLP)
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
To automatically analyze linguistic features of each words in their corresponding
sentence, we employed the Python package spaCy \citep{spacy2} and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
Non-speech vocalizations were dropped from the sentences before analysis.
We performed analyses regarding part-of-speech (i.e. grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e. multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e. if the word is part of a stop list).
